### 2014-04-16 doc/uist14/applications.tex
fixes, changes to application

Though such head orientation targeting enables a wide range of context-aware applications, in this paper we focus on our GlassRemote system that we have built using the existing hardware platform to achieve a universal smart appliance control functionality.

The huge benefit using head orientation is to solve two challenges that exist in most commercial list-based solutions -- {\em naming} and {\em scoping}. First, assigning clear names is non-trivial. Especially in shared spaces, the person trying to control the device might not be the one that named it - e.g., while an office building manager may know what ``Light 4 in area E'' corresponds to, an occupant may not. Second, without a method of scoping selection to automatically filter non-relevant devices, paging though long lists of names or navigating hierarchies becomes potentially more cumbersome than the physical action that the ``convenient'' software solution was meant to replace. Our head-orientation based interaction elegently solves these two problems.

In order to control a smart appliance, the user performs a physical target selection (scan, refine and confirm) first and then the appliance-specific UI will be shown in the near-eye display.

@@

To assess the usability of such applications when the novel interaction scheme is added, we have built a few smart appliances (including a fan, a lamp and a TV, Figure~\ref{fig:smart-home}) and asked 14 participants to work through a concrete smart home scenario. The fan and lamp are relatively dumb and only support turning-on and turning-off. The smart TV provides control capability of switching the channels and adjust the volumn, as well as pause/play. From this study, we report some of the qualitative results to strength our motivation for the head-orientation interaction.

\ben{Will add more from our survey.}
During the study, all participants have successfully completed the list of tasks. They commented positively on the universal remote control functionality (e.g., \studyquote{I didn't have to search for different remote controllers for different appliances}) and stated it was easy to target and connect to appliances, in line with the findings of the previous study procedure. Participants saw benefits of the device for families --- \studyquote{It might also be useful for people who need to take care of small children that they can complete all the tasks while keeping an eye on their children at the same time}, though settings that require more movement than watching a movie at home (e.g., cooking) may be more appropriate scenarios for wearing the device.

>>>>

Head orientation targeting can enable a wide range of context-aware applications. We implement one particular demonstrative application: a universal smart appliance controller. Users select a smart device (e.g., light fixture, TV, or home appliance) with Glass --- upon confirming the selection, an appliance-specific UI is shown on the user's near-eye display, and they can control the application (without having to continually look at it) through their device touchpad.

We implemented a prototype of this remote controller for three physical devices: a lamp and fan that could be switched on or off; and a smart TV control with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). We switched discrete appliances using relays, and implemented the smart TV with a laptop connected to a 30\inch{} display. User interfaces for each were pre-defined in our application.

We set the devices up in a simulated living room environment and invited 14 users to step through a predefined set of tasks to control the appliances at a distance.

%The huge benefit using head orientation is to solve two challenges that exist in most commercial list-based solutions -- {\em naming} and {\em scoping}. First, assigning clear names is non-trivial. Especially in shared spaces, the person trying to control the device might not be the one that named it - e.g., while an office building manager may know what ``Light 4 in area E'' corresponds to, an occupant may not. Second, without a method of scoping selection to automatically filter non-relevant devices, paging though long lists of names or navigating hierarchies becomes potentially more cumbersome than the physical action that the ``convenient'' software solution was meant to replace. Our head-orientation based interaction elegently solves these two problems.

%In order to control a smart appliance, the user performs a physical target selection (scan, refine and confirm) first and then the appliance-specific UI will be shown in the near-eye display.

@@

%To assess the usability of such applications when the novel interaction scheme is added, we have built a few smart appliances (including a fan, a lamp and a TV, Figure~\ref{fig:smart-home}) and asked 14 participants to work through a concrete smart home scenario. The fan and lamp are relatively dumb and only support turning-on and turning-off. The smart TV provides control capability of switching the channels and adjust the volumn, as well as pause/play. From this study, we report some of the qualitative results to strength our motivation for the head-orientation interaction.

\ben{Will add more from our survey.}
All participants successfully completed the list of tasks. They commented positively on the universal remote control functionality (e.g., \studyquote{I didn't have to search for different remote controllers for different appliances}) and stated it was easy to target and connect to appliances, in line with the findings of the previous study procedure. Participants saw benefits of the device for families --- \studyquote{It might also be useful for people who need to take care of small children that they can complete all the tasks while keeping an eye on their children at the same time}, though settings that require more movement than watching a movie at home (e.g., cooking) may ultimately be more compelling scenarios for wearing the device around the home.

### 2014-04-16 doc/uist14/interaction.tex
fixes, changes to application

Though IR signal has enabled us achieve head orientation-based targeting (simplex communication), we envision that more complicated applications could be built on top. Therefore, we added 802.15.4 radio to Glass and all the target nodes.

>>>>

While we use IR signal to establish simplex point-to-point communication from Glass to a target, we envision that more complicated applications can be built on top of the selection functionality. Therefore, we added 802.15.4 radios to Glass and all the target nodes to enable bi-directional communication between all nodes and Glass. \bjoern{not entirely correct - we also need node-to-glass communication for the Intensity IR technique.}

### 2014-04-16 doc/uist14/iteration3.tex
fixes, changes to application

%!TEX root = uist14.tex
\section{Iteration 3: Head motion refinement}
\label{sec:iteration-3:-head}
\subsection{Problem Statement and Goal}
Both{\em Naive IR} and {\em Intensity IR} rely on list navigation on the near-eye display for the refinement step. This has two problems: First, a spatial layout of targets is compressed into a uni-dimensional list. List navigation commands thus have poor spatial mapping. Second, our techniques require the user to switch their focus back and forth between the physical world and the display. These issues motivated us to design an approach that also utilizes orientation information during the {\em refinement} stage, to provide a more direct mapping between the user's actions and target selection.

>>>>

%!TEX root = uist14.tex
\section{Iteration 3: Head motion refinement}
\label{sec:iteration-3:-head}
\subsection{Problem Statement and Goal}
Both {\em Naive IR} and {\em Intensity IR} rely on list navigation on the near-eye display for the refinement step. This has two problems: First, a spatial layout of targets is compressed into a uni-dimensional list. List navigation commands thus have poor spatial mapping. Second, our techniques require the user to switch their focus back and forth between the physical world and the display. These issues motivated us to design an approach that also utilizes orientation information during the {\em refinement} stage, to provide a more direct mapping between the user's actions and target selection.
